State Results

### 2023-07-18 reports/state_figures.Rmd
add dotted line at model change (state level)

dates %>% 
  group_by(biweek) %>%
  summarize(mindate=min(date),maxdate=max(date))

@@

subset %>%
   # mutate(vlabel = gsub("$\\,$CTIS Priors that Do Not Vary by State or Date$\\,$",
   #                     "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", as.character(vlabel))) %>% 
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub,
             fill = 'Probabilistic Bias Analysis'),
             alpha = .8,
             show.legend=FALSE) +
  geom_ribbon(aes(x = date,
                  fill = 'Covidestim',
                  ymin = infections.lo,
                  ymax = infections.hi),
              alpha = .6) +
  facet_wrap(~name, ncol=4, scales = "free",
              labeller= labeller(vlabel =as_labeller(TeX, default=label_parsed))) +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3.5 months", 
               date_labels = "%b %Y") +
  theme_c(axis.text.x=element_text(size=7),
          axis.text.y = element_text(size=4.5),
          legend.position = "top",
          legend.text=element_text(size=12),
          strip.text.x=element_text(size=11,
                                    face='plain',
                                    color='white')) +
  scale_fill_manual(values =comp_state_pal, name='')  +
  labs(y = "Estimated Infections",
       title = paste0("Estimated Infections by State")) +
  guides(color = guide_legend(override.aes = list(linewidth =2),
                              nrow=2,
                              byrow=TRUE))

>>>>

# last biweek for first model is biweek 24
last_biweek_old_model <- dates %>% 
  group_by(biweek) %>%
  summarize(mindate=min(date),maxdate=max(date))  %>%
  filter("2021-11-30" >= mindate & "2021-11-30" <= maxdate)

cat("Last two week interval with previous model was biweek", last_biweek_old_model$biweek,
    "\ndates", paste0("(", last_biweek_old_model$mindate, ", ",
                    last_biweek_old_model$maxdate, ")"))

end_old_model <- last_biweek_old_model$maxdate

@@

subset %>%
   # mutate(vlabel = gsub("$\\,$CTIS Priors that Do Not Vary by State or Date$\\,$",
   #                     "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", as.character(vlabel))) %>% 
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub,
             fill = 'Probabilistic Bias Analysis'),
             alpha = .8,
             show.legend=FALSE) +
  geom_ribbon(aes(x = date,
                  fill = 'Covidestim',
                  ymin = infections.lo,
                  ymax = infections.hi),
              alpha = .6) +
  geom_vline(xintercept=end_old_model,
             linetype=2,
             color="darkred",
             linewidth=.5) +
  facet_wrap(~name, ncol=4, scales = "free",
              labeller= labeller(vlabel =as_labeller(TeX, default=label_parsed))) +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3.5 months", 
               date_labels = "%b %Y") +
  theme_c(axis.text.x=element_text(size=7),
          axis.text.y = element_text(size=4.5),
          legend.position = "top",
          legend.text=element_text(size=12),
          strip.text.x=element_text(size=11,
                                    face='plain',
                                    color='white')) +
  scale_fill_manual(values =comp_state_pal, name='')  +
  labs(y = "Estimated Infections",
       title = paste0("Estimated Infections by State")) +
  guides(color = guide_legend(override.aes = list(linewidth =2),
                              nrow=2,
                              byrow=TRUE))
